\textbf{ Interpretable Gaussian Processes for Stellar Variability }

### 2021-01-15 tex/ms.tex
more text

@@

The method presented in this paper may be thought of as a synthetic likelihood
method in the limit of an infinite number of forward model samples. Unlike
\citet{Wood2010}, whose method determines the mean and covariance of the
distribution of $f$ conditioned on $\pmb{\theta}$ by sampling, we are able
to actually compute the mean and covariance of $f$ \emph{in closed form}.
Unlike traditional SL methods, which are inherently noisy, our method employs
the \emph{exact} Gaussian approximation to the likelihood function.

Our GP is also closely related to techniques commonly employed in models
of the cosmic microwave background. In particular, it is a type of
Gaussian random field (GRF) on the sphere \citep{Wandelt2012} \xxx{...}

Finally, our method is also related to various families of approximate inference, such as
variational inference (VI), in which a multivariate Gaussian is used to
approximate the \emph{posterior} distribution, or to approximate Bayesian
computation (ABC) \xxx{...}

\xxx{TODO: Discuss \citet{Basri2020}, how we agree and disagree. Compare to Brett's
    paper using ABC to measure spot sizes as a function of spectral type.}

>>>>

\subsubsection{GPs, GRFs, and approximate inference}

@@

The method presented in this paper may be thought of as a synthetic likelihood
method in the limit of an infinite number of forward model samples. Unlike
\citet{Wood2010}, whose method determines the mean and covariance of the
distribution of $f$ conditioned on $\pmb{\theta}$ by sampling, we are able
to actually compute the mean and covariance of $f$ \emph{in closed form}.
While traditional SL methods are inherently noisy, our method employs
the \emph{exact} Gaussian approximation to the likelihood function.

Our GP is also closely related to techniques commonly employed in models
of the cosmic microwave background (CMB). In particular, it is a type of
Gaussian random field (GRF) on the sphere, which are frequently used to
model perturbations in the CMB \citep{Wandelt2012}. In general, however,
GRFs used in cosmology are isotropic: when expressed in the spherical
harmonic basis, their covariance matrix is diagonal and admits a
representation as a (one-dimensional) power spectrum. Our GP, in contrast,
is anisotropic in
the polar coordinate (i.e., the latitude) by construction.

Our method is also related to various families of approximate inference, such as
variational inference (VI), in which a multivariate Gaussian is used to
approximate the \emph{posterior} distribution \citep[e.g,][]{Blei2016},
or to approximate Bayesian
computation (ABC), in which an (often intractable) likelihood function is
replaced with an approximation computed from simulations from the prior
\citep[e.g.,][]{Beaumont2019}.

\xxx{Finally, talk about \citet{Perger2020} on interpretable GPs}.

\subsubsection{Spots and stellar variability}

\xxx{%
    \citet{Morris2020} uses the ``smoothed amplitude'', the difference between the
    maximum and minimum flux in a de-trended light curve, as the summary statistic
    in ABC. Try to infer spot coverage fractions. But this is \emph{not an
        observable}. Note that his contrast $c'$ is defined in the opposite sense
    as ours (our $c = 1 - c'$.)
}

\xxx{%
    \begin{itemize}
        \item Discuss \citet{Basri2020}, how we agree and disagree.
        \item Discuss \citep{Morris2020} on ABC to measure spot sizes as a function of spectral type.
        \item Discuss \citep{Jackson2013}.
        \item Discuss \citep{Mazeh2015}.
    \end{itemize}
}
